### 2017-12-11 submission/manuscript.Rmd
refine chimera section -- closer to final edit

# Read in chimera prevalence results
kruskal_chimera_prev <- read_csv("../data/process/tables/mock_chimera_overall_kruskal_results.csv")
dunn_chimera_prev <- read_csv("../data/process/tables/mock_chimera_overall_dunn_results.csv")

@@

***Chimeric Sequences Corelate with OTUs and are HiFi Taq Dependent:***
After chimera removal using VSEARCH and removal of sequences that did not classify as bacteria we assessed the percentage of sequences that were still chimeric within our mock community. From this we observed that Platinum HiFi conssitently had the highest percentage of chimeric reads regardless of amplification cycle number and sub-sampling depth [Figure 4]. For all Taqs a positive correlation was observed between chimeric sequences and number of OTUs and this correlation was strongest for Platinum and Phusion HiFi Taq [Figure 5]. In general the correlations between the number of OTUs and chimeric sequences became stronger as sub-sampling depth increased [Figure 5].

>>>>

# Read in chimera prevalence results
kruskal_chimera_prev <- as.data.frame(read_csv("../data/process/tables/mock_chimera_overall_kruskal_results.csv"))
dunn_chimera_prev <- read_csv("../data/process/tables/mock_chimera_overall_dunn_results.csv")

@@

***Chimeric Sequences Corelate with OTUs and are HiFi Taq Dependent:***
After chimera removal using VSEARCH and removal of sequences that did not classify as bacteria we assessed the percentage of sequences that were still chimeric within our mock community. At all levels of sub-sampling and cycle number there were significant differences between the HiFi Taq used (P-value `r ifelse(max(filter(kruskal_chimera_prev, sub_sample_level > 500)[, "bh"]) < 0.05, invisible("<"), invisible("check data"))` 0.05) [Table S9]. Using a Dunn's post-hoc test the vast majority of these differences were driven by Platinum being different then all other HiFi Taq across cycle number and sub-sampling depth [Table S10]. Generally, across sub-sampling depth and cycle number Accuprime^TM^ had the lowest chimera prevalence of all the HiFi Taq [Figure 4].

For all Taqs a positive correlation was observed between chimeric sequences and number of OTUs with this correlation being strongest for Platinum and Phusion HiFi Taq [Figure 5]. In general, the R^2^ value between the number of OTUs and chimeric sequences became stronger as sub-sampling depth increased [Figure 5]. Interestingly, Accuprime^TM^ not only had one of the lowest chimera prevalence but also consistently had the lowest correlations between the number of OTUs and chimeric sequences [Figure 5].

### 2017-12-11 submission/manuscript.tex
refine chimera section -- closer to final edit

\textbf{\emph{Chimeric Sequences Corelate with OTUs and are HiFi Taq
Dependent:}} After chimera removal using VSEARCH and removal of
sequences that did not classify as bacteria we assessed the percentage
of sequences that were still chimeric within our mock community. From
this we observed that Platinum HiFi conssitently had the highest
percentage of chimeric reads regardless of amplification cycle number
and sub-sampling depth {[}Figure 4{]}. For all Taqs a positive
correlation was observed between chimeric sequences and number of OTUs
and this correlation was strongest for Platinum and Phusion HiFi Taq
{[}Figure 5{]}. In general the correlations between the number of OTUs
and chimeric sequences became stronger as sub-sampling depth increased
{[}Figure 5{]}.

>>>>

\textbf{\emph{Chimeric Sequences Corelate with OTUs and are HiFi Taq
Dependent:}} After chimera removal using VSEARCH and removal of
sequences that did not classify as bacteria we assessed the percentage
of sequences that were still chimeric within our mock community. At all
levels of sub-sampling and cycle number there were significant
differences between the HiFi Taq used (P-value \textless{} 0.05)
{[}Table S9{]}. Using a Dunn's post-hoc test the vast majority of these
differences were driven by Platinum being different then all other HiFi
Taq across cycle number and sub-sampling depth {[}Table S10{]}.
Generally, across sub-sampling depth and cycle number
Accuprime\textsuperscript{TM} had the lowest chimera prevalence of all
the HiFi Taq {[}Figure 4{]}.

For all Taqs a positive correlation was observed between chimeric
sequences and number of OTUs with this correlation being strongest for
Platinum and Phusion HiFi Taq {[}Figure 5{]}. In general, the
R\textsuperscript{2} value between the number of OTUs and chimeric
sequences became stronger as sub-sampling depth increased {[}Figure
5{]}. Interestingly, Accuprime\textsuperscript{TM} not only had one of
the lowest chimera prevalence but also consistently had the lowest
correlations between the number of OTUs and chimeric sequences {[}Figure
5{]}.
